\documentclass{article}

\title{Proposal}
\author{Mir Patel (MDP210002) \and Maunika Achanta (MXA210108) \and Tushar Wani (TMW220003)}
\date{\today}

\begin{document}
\maketitle

\section{Overall Goal}
The goal is to provide a personal professional chef for everyone to help them cook their meals. The system will mainly be a voice agent like Google Assistant or Amazon Alexa. The differentiating factor is that our system will have the entire context of the recipe while giving answers to questions and instructing steps. We hypothesize that our system will be dramatically more helpful as compared to traditional voice agents like Google Assistant.

\section{Scope}
We will work on implementing the system to support any recipes for one cusine. The system will be able to adapt to user's preferences such as their health restrictions and taste preferences. One way to adapt will be by suggesting substitutions for ingredients. While cooking, the system will be able to proactively suggest timers for time sensitive steps. Be able to traverse through the recipe using relative numbering. For example, "What was the previous step?" or "What is the step after the next one?"

\section{Workload}
\subsection{Maunika}
\begin{itemize}
  \item Work on figuring out how the substitution graph will be build and used as a rag implementation for the model to utilize
  \item Figure out how to find/scrape various small tutorials for tools that will be required for chosen cursine
\end{itemize}

\subsection{Mir}
\begin{itemize}
  \item Find possible LLM models/APIs that can be used for this application
  \item Figure out a good way to implement regression testing for the project
\end{itemize}

\subsection{Tushar}
\begin{itemize}
  \item Figure out how to implement the APIs into a NuxtJS based web application
  \item Figure out how to run a web scaper inside of the backend of the web application
\end{itemize}
\end{document}